Propensity Estimation Matrix Factorization Through Mixed-Quantized Dataset

### 2022-07-29 paper/paper.tex
Add algo

\newcommand{\vect}[1]{\boldsymbol{#1}}
\newcommand{\mb}[1]{\mathbf{#1}}
\def\RR{\mathbb{R}}
\def\ZZ{\mathbb{Z}}
\def\EE{\mathbb{E}}
\def\PP{\mathbb{P}}
\def\QQ{\mathbb{Q}}
\def\II{\mathbb{I}}
\def\CC{\mathbb{C}}
\def\NN{\mathbb{N}}
\def\OO{\mathbb{O}}
\def\HH{\mathbb{H}}
\def\Ll{\mathcal{L}}
\def\Mm{\mathcal{M}}

@@

>>>>

\newcommand{\vect}[1]{\boldsymbol{#1}}
\newcommand{\mb}[1]{\mathbf{#1}}
\def\RR{\mathbb{R}}
\def\ZZ{\mathbb{Z}}
\def\EE{\mathbb{E}}
\def\PP{\mathbb{P}}
\def\QQ{\mathbb{Q}}
\def\II{\mathbb{I}}
\def\CC{\mathbb{C}}
\def\NN{\mathbb{N}}
\def\OO{\mathbb{O}}
\def\HH{\mathbb{H}}
\def\Ll{\mathcal{L}}
\def\Mm{\mathcal{M}}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

\[ \argmin_{V,W,A} \frac{1}{N}\left(\frac{(Y_{u,i}- (V_u^TW_i + A))^2}{P_{u,i}} \right) + c \Vert A \Vert^2\]
where $A = \{ b_u, b_i, \mu \}$ represents the standard bias parameters (offset), $\hat{Y} = V_u^TW_i + A$ is the predicted rating, and $c \Vert A \Vert^2$ is the regularizer.

Stochastic gradient descent (SGD) step for one sample rating $(i,j)$:
\[ b_u \gets b_u - \alpha(b_u - \frac{1}{P_{i,j}}(r_{i,j} - \hat{r}_{i,j})) \]
\[ b_i \gets b_i - \alpha(b_i - \frac{1}{P_{i,j}}(r_{i,j} - \hat{r}_{i,j})) \]
\[ V_i \gets V_i - \alpha(V_i - \frac{1}{P_{i,j}}W_j(r_{i,j} - \hat{r}_{i,j})) \]
\[ W_j \gets W_j - \alpha(W_j - \frac{1}{P_{i,j}}V_i(r_{i,j} - \hat{r}_{i,j})) \]
where $\alpha$ is the learning rate, which can be tuned independently for each parameter. In our experiments, we fix $\alpha$ across parameters.
